pema application

### 2022-11-19 paper/manuscript.Rmd
update 2022-11-19 10:59:30

Meta-analysis is a quantitative form of evidence synthesis,
whereby effect sizes from multiple similar studies are aggregated.
In its simplest form, this aggregation consists of a weighted average of the observed effect sizes.
Weighting accounts for the fact that some observed effect sizes are assumed to be more informative about the underlying population effect.
<!-- Each effect size is assigned a weight that determines how influential it is in calculating the summary effect. -->
The weights are based on specific assumptions;
for example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect.
This assumption is well-suited to the situation where effect sizes from close replication studies are meta-analyzed [@higginsReevaluationRandomeffectsMetaanalysis2009]. 
The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
Each observed effect size provides information about the mean and standard deviation of this distribution of population effect sizes.
This assumption is more appropriate when studies are conceptually similar and differences between them are random [@higginsReevaluationRandomeffectsMetaanalysis2009].

Not all heterogeneity in effect sizes is random, however.
Quantifiable between-study differences may introduce systematic heterogeneity.
Such between-study differences are known as "moderators".
For example, if studies have been replicated in Europe and the Americas, this difference could be captured by a binary moderator called "continent".
Alternatively, if studies have used different dosages of the same drug, this may be captured by a continuous moderator called "dosage".
Systematic heterogeneity in the observed effect sizes can be accounted for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
This technique provides estimates of the effect of one or more study characteristics on the overall effect size,
as well as of the overall effect size and residual heterogeneity after controlling for their influence.

One common application of meta-analysis is to summarize existing bodies of literature.
In such situations, the number of moderators is often relatively high because similar research questions have been studied in different laboratories,
using different methods, instruments, and samples.
Each of these between-study differences could be coded as a moderator, and some of these moderators may explain systematic heterogeneity.

The influence of multiple moderators can be accounted for using meta-regression.
However, like any regression-based approach, meta-regression requires a relatively high number of cases (studies) per parameter to obtain sufficient power to examine heterogeneity.
In applied meta-analyses, the number of available studies is often too low to examine heterogeneity reliably [@rileyInterpretationRandomEffects2011].
At the same time, there are many potential sources of heterogeneity,
as similar research questions are studied in different laboratories, using different methods,
instruments, and samples.
This leads to a problem known as the "curse of dimensionality": the number of candidate moderators is large relative to the number of cases in the data.
<!-- This poses a challenge in the -->
<!-- classic meta-analysis paradigm, which, like any regression-based approach, requires a -->
<!-- high number of cases per parameter.  -->
Between-studies differences present a non-trivial challenge to data aggregation
using classic meta-analytic methods.
At the same time, they also provide an unexploited
opportunity to learn which differences between studies have an impact on the effect size
found, if adequate exploratory techniques are used.

Addressing this curse of dimensionality necessitates *variable selection*:
the selection of a smaller subset of relevant moderators from a larger number of candidate moderators.
One way to perform variable selection is by relying on theory.
However, in many fields of science, theories exist at the individual level of analysis (e.g., in social science, at the level of individual people).
These theories do not necessarily generalize to the study level of analysis.
Using theories at the individual level for moderator selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
To illustrate what a theory at the study level of analysis might look like, 
consider the so-called *decline effect*.
It is a phenomenon whereby effect sizes in a particular tranche of the literature seem to diminish over time [@schoolerUnpublishedResultsHide2011].
It has been theorized that the decline effect can be attributed to regression to the mean:
A finding initially draws attention from the research community because an anomalously large effect size has been published, and subsequent replications find smaller effect sizes.
Based on the decline effect, we might thus expect the variable "year of publication" to be a relevant moderator of study effect sizes.
Note that this prediction is valid even if year is orthogonal to the outcome of interest within each study.
Until more theory about the drivers of between-study heterogeneity is developed,
however, this approach will have limited utility for variable selection.
<!--A second example that might illustrate this problem is a study that concluded that American college students' empathy had decreased over time, based on meta-analysis of 72 samples collected between 1979 and 2009.-->

An alternative solution is to rely on statistical methods for variable selection.
This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
There is precedent for the use of machine learning to perform variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
This work used the *random forest* algorithm; a non-parametric approach that largely ignores irrelevant moderators.
One limitation of random forests is that non-parametric models are harder to interpret,
particularly for a readership that is accustomed to linear models,
where the effect of each predictor is described by a single parameter.
An alternative method for variable selection that can be used in linear models is *regularization*:
shrinking model parameters towards zero, such that irrelevant moderators are eliminated.
The present paper introduces *Bayesian regularized meta-regression* (BRMA),
an algorithm that uses Bayesian estimation with regularizing priors to perform variable selection in meta-analysis.
Regularizing priors assign a high probability mass to near-zero values,
which keeps small regression coefficients close to zero, resulting in a sparse solution.
This manuscript discusses two shrinkage priors,
the LASSO and horseshoe prior.
<!--
Thus, there is a need of a regularization method to curtail overfitting. Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection. The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for regularized meta-regression.
This dilemma could be resolved by an exploratory technique that can identify relevant moderators in meta-analysis,
and which is relatively robust to small sample sizes.
-->
<!--Such shrinkage is advantageous because it performs variable selection and results in a sparse model.
Sparse models are easier to interpret, as fewer non-zero effects remain.
Regularization also provides a solution to the curse of dimensionality; unlike standard regression models, it can provide identified models even if the number of moderators exceeds the number of cases.-->
<!--By doing this it automatically performs variable selection. It does not seem to be immediately clear why shrinking the coefficients should be an improvement to the model. However, by shrinking the parameters, it lowers the variance of the model by increasing the bias only a little bit. In other words, the model sacrifices some of its ability to fit the current data, to greatly increase the ability to predict future data with the same fit (James et al., 2013). This is better known as the bias/variance tradeoff (Briscoe & Feldman, 2011).-->

@@

To understand how BRMA estimates the relevant parameters and performs variable selection, it is instructional to first review the statistical underpinnings of the aforementioned classic approaches to meta-analysis.
First is the fixed-effect model, which assumes that each observed effect size $T_i$ is an estimate of an underlying true effect size $\Theta$ [@hedgesFixedRandomeffectsModels1998].
The only cause of heterogeneity in observed effect sizes is presumed to be effect size-specific sampling variance, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
Thus, for a collection of $k$ studies, the observed effects sizes of individual studies $i$ (for $i$ = 1,2, . . . $k$) are given by:

@@

<!--
\begin{aligned}
y_i &= \theta_i + \epsilon_i &\text{where } \epsilon_i \sim N(0, \sigma^2_i)\\ % \text{ and } 
%\theta_1 &= \theta_2 \dots = \theta_k
\end{aligned}-->

Under the fixed effect model, the estimated population effect size  $\hat{\theta}$ is obtained by computing a weighted average of the observed effect sizes.
If sampling error is assumed to be the only source of variance in the observed effect size,
then it follows that studies with smaller standard errors estimate the underlying true effect size more precisely<!--(Schmidt, Oh \& Hayes, 2009)-->.
The fixed-effect weights are thus simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
The estimate of the true effect is a weighted average across observed effect sizes:

@@

<!--A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014). Caused by differences in for example cultures of research populations and used methods or instruments (Neuman, 2011). Even in replication studies there are sometimes moderators that are unanticipated (Kunert, 2016). This leads very often to an eventual poor performance of the fixed-effects meta-analysis model (Snijders, 2005). -->

Whereas the fixed-effect model assumes that only one true population effect exists,
the random-effects model assumes that true effects may vary for unknown reasons,
and thus follow a (normal) distribution of their own [@hedgesFixedRandomeffectsModels1998].
This heterogeneity of the true effects is represented by their variance, $\tau^{2}$.
The random effects model thus assumes that the heterogeneity in observed effects can be decomposed into sampling error and between-studies heterogeneity, resulting in the following equation for the observed effect sizes:

@@

In this model, $\Theta$ is the mean of the distribution of true effect sizes, and $\tau^2$ is its variance, which can be interpreted as the variance between studies.

If the true effect sizes follow a distribution, 
then even less precise studies (with larger sampling errors) may provide some information about this distribution.
Like fixed-effect weights, random effects weights are still influenced by sampling error, but this influence is attenuated by the estimated variance of the true effect sizes. 
The random-effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
It is important to note that,
whereas the sampling error for each individual effect size is treated as known, the
between-study heterogeneity $\tau^{2}$ must be estimated.
This estimate is represented by $\hat{\tau}^{2}$.

### Meta-regression

The random-effects model assumes that causes of heterogeneity in the true effect sizes are unknown, and that their influence is random.
Oftentimes, however, there are systematic sources of heterogeneity in true effect sizes.
These between-study differences can be coded as moderators, and their influence can be estimated and controlled for using meta-regression.
Meta-regression with $p$ moderators can be expressed with the following equation, where $x_{1\ldots p}$ represent the moderators, and $\beta_{1\ldots p}$ the regression coefficients:

@@

Note that $\beta_0$ represents the intercept of the distribution of true effect sizes after controlling for the moderators
and the error term $\zeta_{i}$ represents residual between-studies heterogeneity.
This term is included because unexplained heterogeneity often remains after accounting for the moderators.
This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random [@lopez-lopezEstimationPredictivePower2014].

<!--
An accurate estimation of the residual heterogeneity contributes to a better interpretation of the effect of the moderators (Panityakul, Bumrungsup \& Knapp, 2013).-->

To solve this model, the regression coefficients and residual heterogeneity must be estimated simultaneously.
<!--The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013). The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis \& Reeves, 2011; Jackson \& White, 2018). Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell \& Gorden, 2001). Considering that all models their performance is linked to the accuracy of the estimate. According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
Numerous methods have been proposed to estimate meta-regression models, the most commonly used of which is restricted maximum likelihood (REML).
REML is an iterative method, meaning it performs the same calculations repeatedly, updating the estimated regression coefficients and residual heterogeneity until these estimates stabilize.
<!--, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method. These methods are mostly divided into two groups: closed-form or non-iterative methods and iterative methods. The main difference between these groups is that the closed form group uses a predetermined number of steps to provide an estimation for the residual heterogeneity, whereas the iterative methods run multiple iteration, as the name suggests, to converge to a solution when a specific criterion is met. It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.-->
This estimator has low bias, which means that the average value of the estimated regression coefficients and residual heterogeneity is close to their true values [@panityakulEstimatingResidualHeterogeneity2013].
<!-- ; (Panityakul et al., 2013; Hardy & Thompson, 1996). -->
However, this bias comes at the cost of higher variance, which means that the estimated values of a population parameter vary more from one sample to the next. 
In practice, an estimator with higher variance generalizes less well to new data.
This phenomenon is known as the *bias-variance trade-off*.
Regularization increases bias to reduce variance.
A disadvantage of this trade-off is that model parameters can no longer be interpreted as straightforwardly as OLS regression coefficients.
An advantage is that the resulting model is more generalizable and makes better predictions for new data [see @hastieElementsStatisticalLearning2009].

@@

Regularized regression biases parameter estimates towards zero.
Before examining the Bayesian case, we will explain the general principle of regularization in frequentist regression.
OLS regression estimates the model parameters by minimizing the Residual Sum of Squares (RSS) of the dependent variable, which is given by:

$$
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
$$
The resulting parameter estimates are those that give the best predictions of the dependent variable in the present data set.
Penalized regression, by contrast, adds a penalty term to the RSS.
One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty [@hastieElementsStatisticalLearning2009],
which corresponds to the sum of their absolute values.
This gives the penalized residual sum of squares:

@@

Because the penalty term is a function of the regression coefficients,
the optimizer is incentivized to keep the regression coefficients as small as possible.
In this equation, $\lambda$ is a tuning parameter that determines how influential the penalty term will be.
If $\lambda$ is zero, the shrinkage penalty has no impact and the penalized regression will produce the OLS estimates.
If $\lambda \to \infty$, all coefficients shrink towards zero, producing the null model.
<!--Another commonly used penalty is the L2-norm of the coefficients, or ridge penalty,
which corresponds to the sum of their squared values: $\sum_{j=1}^{p}\beta_{j}^2$.-->
Generally, cross-validation is used to find the optimal value for the penalty parameter $\lambda$.
<!--The LASSO penalty has the unique property of shrinking some coefficients to be exactly zero,
but the ridge penalty does not do so, as -->
Note that the LASSO penalty is but one example of a shrinkage penalty; other penalties exist.

<!--The Lasso shrinkage method is not the only shrinkage method, there do exist some others. Nevertheless, the lasso is in the case the best option. It possesses, as opposed to other methods, the ability to shrink the parameter not towards zero, but to be exactly zero (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008). This means that the lasso can perform variable selection, something that is specifically aimed for in this study. -->

<!--
**Alternative to linear model: Tree Based models**
An alternative that can perform variable selection, are tree-based models. These kinds of models have numerous other advantages over linear models. Tree-based models can be used for any data type, are easy to represent visually, require little data preparation and got larger power than linear regressions when moderators exceed observations in quantity. They are also more flexible in handling moderator interactions and non-linearity. As a result of that, they are better in modelling the complicated nature of human behaviour (Earp \& Trafimow, 2015). Decision trees split from the top down and group data in so-called ‘sub-nodes’, in which the data’s aspects are most homogeneous. The goal is to split to get the sub-nodes as uniform as possible, which can be until fully homogenous groups, or if a pre-specified touchstone is reached. 
Still, singletree based models have some limitations. First of all, tree models are unstable, small fluctuations that are utilized to make the model have a possibility to lead to considerable alterations in the constructions of the tree (Dwyer \& Holte, 2007). Second, it has problems with seizing linearity, because it only makes ‘twofold splits’ (Steyerberg, 2019). At last, tree-based models are susceptible to overfitting (Hastie et al, 2009).

There are also more complex tree-based models, known as random-forests, which surmount most of the disadvantages of singletree. This variant incorporates multiple decision trees, and combines results from those trees to create a single model with a more accurate estimate (Breiman, 2001). The essential idea behind is know as the ‘wisdom of crowds’, a large number of relatively uncorrelated trees operating as a group will outperform any of the individual elements. The somewhat low correlation between the models is fundamental, because uncorrelated models are able to produce ensemble predictions with a higher accuracy that any individual prediction. This is because the trees preserve each other from their own singular errors (Genuer, Poggi \& Tuleau-Malot, 2010). The lower tendency to overfitting is another advantage of random forests over single trees (Bühlmann \& Yu, 2002). As well as the possibility to predict cases that are not components of the bootstrap sample of the tree. This kind of measure is known as out-of-bag error, which is an approximation of the cross-validation error, and provides proper estimates of the prediction accuracy in further samples (Hastie et al., 2009). 
An alternative to explore heterogeneity in meta-analysis with a singletree-based method is MetaForest. A technique developed by van Lissa (2017), designed to overcome the lacking’s of singletrees by using random forests. MetaForest applies random-effects or fixed-effects weights to random forests.
Based on two simulation studies, van Lissa (2017) examined the performance of fixed-effects, random-effects and unweighted MetaForest.

@@

One alternative to the use of a shrinkage penalty is Bayesian estimation with a regularizing prior.
Whereas classical, frequentist estimation relies solely on the data at hand,
Bayesian estimation combines information from the data with a *prior distribution*.
The prior distribution is a probability distribution that reflects expectations about likely parameter values.
This prior is updated with the likelihood of the data to form a posterior distribution,
which reflects expectations about likely parameter values after having seen the data.

A regularizing prior distribution reflects the expectation that not all regression coefficients are substantial enough to be included in the model.
There are many different regularizing prior distributions [@vanErpOberskiMulder2019].
Some of these result in exactly the same solutions as frequentist penalized methods.
For example, applying an independent double exponential (i.e., Laplace) prior to regression coefficients results in posterior modes that are equal to the classical LASSO estimates [@ParkCasella2008].
Other distributions have been developed specifically for the purpose of providing good shrinkage properties,
meaning that the prior pulls small regression coefficients towards zero,
while leaving larger regression coefficients mostly unaffected. 
A popular prior in this regard is the horseshoe prior [@CarvalhoPolsonScott2010].
It has heavier tails than the LASSO prior,
which means that it does not shrink (and therefore bias) substantial coefficients as much.

### Implementation

>>>>

Meta-analysis is a quantitative form of evidence synthesis,
whereby effect sizes from multiple similar studies are aggregated.
In its simplest form, this aggregation consists of a weighted average of the observed effect sizes.
Weighting accounts for the fact that some observed effect sizes are assumed to be more informative about the underlying population effect.
<!-- Each effect size is assigned a weight that determines how influential it is in calculating the summary effect. -->
The weights are based on specific assumptions;
for example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect.
This assumption is appropriate when meta-analyzing effect sizes from close replication studies [@higginsReevaluationRandomeffectsMetaanalysis2009]. 
The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
<!-- Each observed effect size provides information about the mean and standard deviation of this distribution. -->
This assumption is more appropriate when studies are conceptually similar but vary in small random ways that introduce heterogeneity in effect sizes [@higginsReevaluationRandomeffectsMetaanalysis2009].

Heterogeneity in effect sizes is not always random, however.
When similar research questions are studied by different labs, in different populations, using different study designs, measurement instruments, and methods - those between-study differences may introduce *systematic heterogeneity*.
Suspected causes of systematic heterogeneity can either be used as exclusion criteria,
or accounted for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
Meta-regression estimates the effect of study characteristics on effect size,
and provides an estimate of the overall effect size and residual heterogeneity after controlling for their influence.
For example, if studies have been replicated in Europe and the Americas,
one could either exclude studies from Europe from further analysis,
or code a binary moderator variable called "continent".
One could then estimate the average effect size across both continents.
Similarly, if studies have examined the effect of a drug at different dosages,
one could code dosage as a continuous moderator, and control for its influence - thus estimating the overall effect size at average dosages.

A common application of meta-analysis is to summarize existing bodies of literature.
In such situations, there are many potentially relevant between-study differences that could be coded as moderators.
Although meta-regression can accommodate multiple moderators,
like any regression-based approach, it requires a relatively high number of cases (studies) per parameter to obtain sufficient statistical power.
In applied meta-analyses, the number of available studies is often too low to obtain sufficient power [@rileyInterpretationRandomEffects2011],
or even so low that the model is not identified [@akaikeNewLookStatistical1974].
This problem is known as the "curse of dimensionality".
<!-- This poses a challenge in the -->
<!-- classic meta-analysis paradigm, which, like any regression-based approach, requires a -->
<!-- high number of cases per parameter.  -->
Between-studies differences thus pose a non-trivial challenge to classic meta-analytic methods.
At the same time, they also provide an unexploited
opportunity to learn which factors impact the effect size
found, if adequate exploratory techniques are used.

The curse of dimensionality can be overcome using *variable selection*:
identifying a smaller subset of relevant moderators from a larger number of candidate moderators [@hastieElementsStatisticalLearning2009].
One way to perform variable selection is by relying on theory, and selecting only moderators that should theoretically have an impact on effect size.
Note, however, that theories at the individual level of analysis do not necessarily generalize to the study level of analysis.
In the social sciences, for example, many theories describe phenomena at the level of individual people.
Using such theories for variable selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
To illustrate what a theory at the study level of analysis might look like, 
consider the so-called *decline effect*.
It is a phenomenon whereby effect sizes in a particular tranche of the literature seem to diminish over time [@schoolerUnpublishedResultsHide2011].
It has been theorized that the decline effect can be attributed to regression to the mean:
A finding initially draws attention from the research community because an anomalously large effect size has been published, and subsequent replications find smaller effect sizes.
Based on the decline effect, we might thus expect the variable "year of publication" to be a relevant moderator of study effect sizes.
Note that this prediction is valid even if year is orthogonal to the outcome of interest within each study.
Until more theory about the drivers of between-study heterogeneity is developed,
however, this approach will have limited utility for variable selection.
<!--A second example that might illustrate this problem is a study that concluded that American college students' empathy had decreased over time, based on meta-analysis of 72 samples collected between 1979 and 2009.-->

An alternative solution is to rely on statistical methods for variable selection.
This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
There is precedent for the use of machine learning to perform variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
This prior work used the non-parametric *random forest* algorithm.
One limitation of random forests is that non-parametric models are harder to interpret,
particularly when the readership is accustomed to linear models that describe the effect of each moderator with a single parameter.

Regularization is a method for variable selection that can be applied in linear models.
It effectively shrinks small model parameters towards zero,
such that irrelevant moderators are eliminated.
The present paper introduces *Bayesian regularized meta-regression* (BRMA),
an algorithm that uses Bayesian estimation with regularizing priors to perform variable selection in meta-analysis.
Regularizing priors assign a high probability mass to near-zero values,
which keeps small regression coefficients close to zero, resulting in a sparse solution.
This manuscript discusses two shrinkage priors,
the LASSO and horseshoe prior.
<!--
Thus, there is a need of a regularization method to curtail overfitting. Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection. The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for regularized meta-regression.
This dilemma could be resolved by an exploratory technique that can identify relevant moderators in meta-analysis,
and which is relatively robust to small sample sizes.
-->
<!--Such shrinkage is advantageous because it performs variable selection and results in a sparse model.
Sparse models are easier to interpret, as fewer non-zero effects remain.
Regularization also provides a solution to the curse of dimensionality; unlike standard regression models, it can provide identified models even if the number of moderators exceeds the number of cases.-->
<!--By doing this it automatically performs variable selection. It does not seem to be immediately clear why shrinking the coefficients should be an improvement to the model. However, by shrinking the parameters, it lowers the variance of the model by increasing the bias only a little bit. In other words, the model sacrifices some of its ability to fit the current data, to greatly increase the ability to predict future data with the same fit (James et al., 2013). This is better known as the bias/variance tradeoff (Briscoe & Feldman, 2011).-->

@@

To understand how BRMA estimates the relevant parameters and performs variable selection,
it is instructional to first review the statistical underpinnings of classical meta-analysis.
As mentioned before, the fixed effect model assumes that each observed effect size $T_i$ is an estimate of an underlying true effect size $\Theta$ [@hedgesFixedRandomeffectsModels1998].
The only cause of heterogeneity in observed effect sizes is presumed to be sampling error, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
Thus, for a collection of $k$ studies,
the observed effects sizes of individual studies $i$ (for $i \in [1,2, \ldots k]$) are given by:

@@

The estimated population effect size $\hat{\theta}$ is then a weighted average of the observed effect sizes.
The assumption that sampling error is the only source of variance in observed effect sizes implies that studies with smaller standard errors estimate the underlying true effect size more precisely and should accrue more weight.
Therefore, fixed effect weights are simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
The estimate of the true effect is a weighted average across observed effect sizes:

@@

<!--A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014). Caused by differences in for example cultures of research populations and used methods or instruments (Neuman, 2011). Even in replication studies there are sometimes moderators that are unanticipated (Kunert, 2016). This leads very often to an eventual poor performance of the fixed effects meta-analysis model (Snijders, 2005). -->

The random effects model assumes that, in addition to sampling error, true effects may vary for random reasons,
and thus follow a (normal) distribution with mean $\Theta$ and variance $\tau^{2}$ [@hedgesFixedRandomeffectsModels1998].
The observed effect sizes are thus given by:

@@

As in the fixed effect model,
studies with smaller sampling errors are assigned more weight.
However, to account for the fact that all studies now provide some information about different regions of the distribution of true effect sizes,
the weights are attenuated in proportion to the spread of that distribution.
The random effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
Whereas sampling error is still treated as known,
the between-study heterogeneity $\tau^{2}$ must be estimated.
This estimate is represented by $\hat{\tau}^{2}$.

Meta-regression extends the random effects model to account for systematic sources of heterogeneity, which are coded as moderators.
The equation below describes a model with $p$ moderators, where $x_{1\ldots p}$ represent the moderators, and $\beta_{1\ldots p}$ their regression coefficients.
Note that $\beta_0$ represents the intercept of the distribution of true effect sizes after controlling for the moderators
and the error term $\zeta_{i}$ represents residual unexplained between-studies heterogeneity.
This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random [@lopez-lopezEstimationPredictivePower2014]:

@@

<!--The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013). The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis \& Reeves, 2011; Jackson \& White, 2018). Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell \& Gorden, 2001). Considering that all models their performance is linked to the accuracy of the estimate. According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
The parameters of this model are the regression coefficients and residual heterogeneity.
Numerous methods have been proposed to estimate meta-regression models,
the most common of which is restricted maximum likelihood (REML).
REML is an iterative method, which means that it repeatedly performs the same calculations and updates the estimated parameters until their estimates stabilize.
<!--, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method. These methods are mostly divided into two groups: closed-form or non-iterative methods and iterative methods. The main difference between these groups is that the closed form group uses a predetermined number of steps to provide an estimation for the residual heterogeneity, whereas the iterative methods run multiple iteration, as the name suggests, to converge to a solution when a specific criterion is met. It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.-->
This estimator has low bias, which means that the average values of the parameters are close to their true values [@panityakulEstimatingResidualHeterogeneity2013].
<!-- ; (Panityakul et al., 2013; Hardy & Thompson, 1996). -->
However, this bias comes at the cost of higher variance, which means that the estimated values of a population parameter vary more from one sample to the next. 
An estimator with low bias and high variance produces results that generalize less well to new data than an estimator with high bias and low variance.
This phenomenon is known as the *bias-variance trade-off*.
Regularization increases bias to reduce variance.
A disadvantage of this trade-off is that model parameters can no longer be interpreted as straightforwardly as OLS regression coefficients.
An advantage is that the resulting model is more generalizable and makes better predictions for new data [see @hastieElementsStatisticalLearning2009].

@@

Ordinary least squares regression (OLS) estimates the model parameters by minimizing the Residual Sum of Squares (RSS) of the dependent variable.
The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data:

$$
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
$$

Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
As an example, we will discuss the most common penalty: the sum of the absolute regression coefficients, also known as the the L1- or LASSO penalty [@hastieElementsStatisticalLearning2009].
Note that other penalties exist.
As the LASSO penalty is a function of the regression coefficients, it increases when they get bigger.
This incentivizes the optimizer to keep the regression coefficients as small as possible.
Note that the amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
If $\lambda$ is zero, the shrinkage penalty has no impact.
If $\lambda \to \infty$,
all coefficients shrink towards zero, producing the null model.
<!--Another commonly used penalty is the L2-norm of the coefficients, or ridge penalty,
which corresponds to the sum of their squared values: $\sum_{j=1}^{p}\beta_{j}^2$.-->
Cross-validation is often used to find the optimal value for the penalty parameter $\lambda$.
<!--The LASSO penalty has the unique property of shrinking some coefficients to be exactly zero,
but the ridge penalty does not do so, as -->
The LASSO penalized residual sum of squares is given by:

@@

<!--The Lasso shrinkage method is not the only shrinkage method, there do exist some others. Nevertheless, the lasso is in the case the best option. It possesses, as opposed to other methods, the ability to shrink the parameter not towards zero, but to be exactly zero (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008). This means that the lasso can perform variable selection, something that is specifically aimed for in this study. -->
<!--
**Alternative to linear model: Tree Based models**
An alternative that can perform variable selection, are tree-based models. These kinds of models have numerous other advantages over linear models. Tree-based models can be used for any data type, are easy to represent visually, require little data preparation and got larger power than linear regressions when moderators exceed observations in quantity. They are also more flexible in handling moderator interactions and non-linearity. As a result of that, they are better in modelling the complicated nature of human behaviour (Earp \& Trafimow, 2015). Decision trees split from the top down and group data in so-called ‘sub-nodes’, in which the data’s aspects are most homogeneous. The goal is to split to get the sub-nodes as uniform as possible, which can be until fully homogenous groups, or if a pre-specified touchstone is reached. 
Still, singletree based models have some limitations. First of all, tree models are unstable, small fluctuations that are utilized to make the model have a possibility to lead to considerable alterations in the constructions of the tree (Dwyer \& Holte, 2007). Second, it has problems with seizing linearity, because it only makes ‘twofold splits’ (Steyerberg, 2019). At last, tree-based models are susceptible to overfitting (Hastie et al, 2009).

There are also more complex tree-based models, known as random-forests, which surmount most of the disadvantages of singletree. This variant incorporates multiple decision trees, and combines results from those trees to create a single model with a more accurate estimate (Breiman, 2001). The essential idea behind is know as the ‘wisdom of crowds’, a large number of relatively uncorrelated trees operating as a group will outperform any of the individual elements. The somewhat low correlation between the models is fundamental, because uncorrelated models are able to produce ensemble predictions with a higher accuracy that any individual prediction. This is because the trees preserve each other from their own singular errors (Genuer, Poggi \& Tuleau-Malot, 2010). The lower tendency to overfitting is another advantage of random forests over single trees (Bühlmann \& Yu, 2002). As well as the possibility to predict cases that are not components of the bootstrap sample of the tree. This kind of measure is known as out-of-bag error, which is an approximation of the cross-validation error, and provides proper estimates of the prediction accuracy in further samples (Hastie et al., 2009). 
An alternative to explore heterogeneity in meta-analysis with a singletree-based method is MetaForest. A technique developed by van Lissa (2017), designed to overcome the lacking’s of singletrees by using random forests. MetaForest applies random effects or fixed effects weights to random forests.
Based on two simulation studies, van Lissa (2017) examined the performance of fixed effects, random effects and unweighted MetaForest.

@@

An alternative to the use of a shrinkage penalty is Bayesian estimation with a regularizing prior.
Bayesian estimation combines information from the data with a *prior distribution*.
The prior distribution assigns a-priori probability to different parameter values.
Likely parameter values have a high probability density, and unlikely parameter values have a low probability density.
The aforementioned (frequentist) approaches, by contrast, treat every possible parameter value as equally plausible.
The prior distribution is updated with the likelihood of the data to form a posterior distribution,
which reflects expectations about likely parameter values after having seen the data [for an extensive introduction, see @mcelreathStatisticalRethinkingBayesian2020].

A regularizing prior distribution shrinks small coefficients towards zero by assigning high probability mass to near-zero values.
There are many different regularizing prior distributions [@vanErpOberskiMulder2019].
Some of these regularizing priors are analogous to specific frequentist methods.
For example, a double exponential prior (hereafter: LASSO prior) results in posterior distributions whose modes are identical to the estimates from LASSO-penalized regression [@ParkCasella2008].

A limitation of the LASSO prior is that it introduces substantial bias in non-zero regression coefficients.
To overcome this limitation, regularizing priors with better shrinkage properties have been developed.
These priors still pull small regression coefficients towards zero,
but exert less bias on larger regression coefficients.
One example is the horseshoe prior [@CarvalhoPolsonScott2010].
It has heavier tails than the LASSO prior,
which means that it does not shrink (and therefore bias) substantial coefficients as much.

The BRMA method introduced here offers both LASSO and horseshoe priors.
The LASSO prior is given by:
$$
\beta_{j} \sim \text{DE}(0, \frac{s}{\lambda})
$$
where DE denotes the double exponential distribution with a location equal to 0 and a scale determined by a global scale parameter $s$ and an inverse-tuning parameter $\lambda$.
In the present study, the global scale parameter is set to 1,
and the inverse-tuning parameter is assigned a $\chi^2$ prior distribution with 1 degree of freedom.
Its value is thus optimized during model estimation.
